A Phenomenological Model for the Intracluster Medium that matches X-ray and Sunyaev-Zel'dovich observations

### 2013-10-03 paper1.tex
text corrected and dereddened

%{\bf As a cautionary remark, we emphasize that our model is only valid within
%$R_{500}$ and more work is needed to extrapolate it to larger cluster
%radii, \qc{particularly for the thermal modeling}.
{\bf As a cautionary remark, \qc{we emphasize that our model is built
to be valid within $R_{500}$ and more work is needed to extrapolate it to 
larger cluster radii, particularly for the thermal modeling}.
Those cluster regions are characterized by a steadily increasing level
of kinetic-to-thermal pressure support \citep[e.g.,][]{2009ApJ...705.1129L,
2012ApJ...758...74B}, density clumping \citep{2011ApJ...731L..10N,
2012arXiv1209.4082B}, and asphericity and ellipticity of the halo
morphologies \citep{2012arXiv1209.4082B}, in particular beyond the virial
radius where the filamentary cosmic web connects to the cluster interiors.}

@@

{\bf In the right panel of Fig.~\ref{fig:SZ_M}, we compare our scaling relation
  to the \qc{recent Atacama Cosmology Telescope (ACT) sample} \citep{2013JCAP...07..008H}, 
  which has a median redshift of $z=0.53$. 
  Again, the slope of our modeled scaling relation is somewhat shallower in comparison
  to the observed slope. Most strikingly, there appears to be a 30 per cent
  offset of the scaling relations, which could be due to a number of reasons. On
  the data side, these could include possible selection effects of the different
  cluster samples or possible biases associated with density clumping and/or
  non-thermal pressure contributions inherited from the X-ray informed
  post-processing that was employed by the ACT Collaboration to construct their
  $Y_{500}$ estimates. This could also indicate that our presented
  model is too simplistic to capture the rich cluster physics and potentially
  may even signal deviations from the assumed self-similar redshift evolution
  (since ACT sample probes on average higher redshift and less massive clusters
  in comparison to the {\em Planck} sample). 
  \qc{However, note that our scaling relation at $z=0.53$ ($A=-27.67\pm0.11$, $B=1.59\pm0.01$) 
  is perfectly compatible within the errors with the one derived from the ACT sample 
  ($A=-28.59\pm2.26$, $B=1.65\pm0.15$).  
  Therefore, we conclude that overall} there is reasonable
  agreement between our phenomenological model and the SZ data of the
  \emph{Planck} and ACT collaborations.}

@@

%However, there are some notable deviations among the different observational
  However, there are \qc{some deviations} among the different observational
  scaling relations and our model, which may either point to observational
  sample selection effects that are not accounted for or missing complexity of
  our model. This model was specifically constructed to provide a reliable
  description of the gas density, which necessarily implies a great match of the
  resulting mock X-ray observables to data (scaling relations and luminosity
  functions) as well as to the low-redshift and massive cluster sample probed by
  {\em Planck}. However, we note that our model has a somewhat shallower slope
  of the $Y_{\rmn{SZ}}-M_{500}$ relation, which implies that the X-ray inferred
  deviations of self-similarity on small scales become weaker on the larger
  scales probed through the SZ effect. Moreover, our model overpredicts the
  normalization of the ACT $Y_{\rmn{SZ}}-M_{500}$ relation (at $z=0.53$) by
  about 30 per cent. This could either indicate possible selection effects of
  the different cluster samples or may even signal a deviation from the assumed
  self-similar redshift evolution. \qc{Nevertheless, we stress that our scaling relation
  is still compatible within the errors of the ACT one.}

>>>>

{\bf As a cautionary remark, we emphasize that our model has been constructed to
  be valid within $R_{500}$ and more work is needed to extrapolate it to larger
  cluster radii, particularly for the thermal cluster emission.  Those cluster
  regions are characterized by a steadily increasing level of kinetic-to-thermal
  pressure support \citep[e.g.,][]{2009ApJ...705.1129L, 2012ApJ...758...74B},
  density clumping \citep{2011ApJ...731L..10N, 2012arXiv1209.4082B}, and
  asphericity and ellipticity of the halo morphologies
  \citep{2012arXiv1209.4082B}, in particular beyond the virial radius where the
  filamentary cosmic web connects to the cluster interiors.}

@@

{\bf In the right panel of Fig.~\ref{fig:SZ_M}, we compare our scaling relation
  to the recent Atacama Cosmology Telescope (ACT) sample
  \citep{2013JCAP...07..008H}, which has a median redshift of $z=0.53$.  Again,
  the slope of our modeled scaling relation is somewhat shallower in comparison
  to the observed slope. Most strikingly, there appears to be a 30 per cent
  offset of the scaling relations, which could be due to a number of reasons. On
  the data side, these could include possible selection effects of the different
  cluster samples or possible biases associated with density clumping and/or
  non-thermal pressure contributions inherited from the X-ray informed
  post-processing that was employed by the ACT Collaboration to construct their
  $Y_{500}$ estimates. This could also indicate that our presented model is too
  simplistic to capture the rich cluster physics and potentially may even signal
  deviations from the assumed self-similar redshift evolution (since the ACT
  sample probes on average higher redshift and less massive clusters in
  comparison to the {\em Planck} sample).  However, note that our scaling
  relation at $z=0.53$ ($A=-27.67\pm0.11$, $B=1.59\pm0.01$) is within the
  uncertainties compatible with that of the ACT sample ($A=-28.59\pm2.26$,
  $B=1.65\pm0.15$).  Thus, we conclude that overall there is reasonable
  agreement between our phenomenological model and the SZ data of the
  \emph{Planck} and ACT collaborations.}

@@

  However, there are some deviations among the different observational scaling
  relations and our model, which may either point to observational sample
  selection effects that are not accounted for or missing complexity of our
  model. This model was specifically constructed to provide a reliable
  description of the gas density, which necessarily implies a great match of the
  resulting mock X-ray observables to data (scaling relations and luminosity
  functions) as well as to the low-redshift and massive cluster sample probed by
  {\em Planck}. However, we note that our model has a somewhat shallower slope
  of the $Y_{\rmn{SZ}}-M_{500}$ relation, which implies that the X-ray inferred
  deviations of self-similarity on small scales become weaker on the larger
  scales probed through the SZ effect. Moreover, our model overpredicts the
  normalization of the ACT $Y_{\rmn{SZ}}-M_{500}$ relation (at $z=0.53$) by
  about 30 per cent. While this offset is still consistent within the 1-$\sigma$
  uncertainty intervals of the ACT scaling relation, this could also indicate
  possible selection effects of the different cluster samples or alternatively
  even signal a deviation from the assumed self-similar redshift evolution.
